Exploiting Non-Slip Wall Contacts to Position\\ Two Particles Using The Same Control Input

### 2019-01-03 journalWallFriction/Conclusion.tex
added stubs for the final journal version.  Still need pictures

  \section*{Appendix}\label{sec:appendix}
 The supplemental material includes four videos:
  	\begin{itemize}	 
 \item Video  \emph{01Model.mov} animates the concepts of uniform control inputs and non-slip boundary contacts.
 \item Video  \emph{02DeltaConfigurationSpace.mp4} demonstrates how the $\Delta$ configuration space is constructed for a variety of workspaces.
 \item Video  \emph{03SimulationWorkSpaces.mp4} shows demonstrations of motion planning in square and disc-shaped workspaces. 
 \item Video  \emph{04Hardware Experiments.mp4} shows an experiment trial moving two particles to goal positions in a small intestine phantom, then an experiment trial using cow stomach tissue.
		\end{itemize}	 	
We also include four  Mathematica Notebooks (.nb files) containing simulation code.  
		   	\begin{itemize}	 
 \item   \emph{SquareWorkSpace.nb} generates paths in a square workspace for two particles.
 \item  \emph{CircularWorkSpace.nb} generates paths in a circular workspace for two particles.
 \item   \emph{DeltaConfigurationSpacePolygon.nb} generates the $\Delta$ configuration space for convex polygons
  \item   \emph{ShortestPathForADisk.nb} analytical solution for shortest path that touches a boundary from one position to another position in a circular workspace.
		\end{itemize}

>>>>

  \section*{Appendix}\label{sec:appendix}
We thank our anonymous reviewers for their advice which improved the presentation and content of this paper, especially the analysis of the reachable sets.
 The supplemental material includes four videos:
  	\begin{itemize}	 
 \item Video  \emph{01Model.mov} animates the concepts of uniform control inputs and non-slip boundary contacts.
 \item Video  \emph{02DeltaConfigurationSpace.mp4} demonstrates how the $\Delta$ configuration space is constructed for a variety of workspaces.
 \item Video  \emph{03SimulationWorkSpaces.mp4} shows demonstrations of motion planning in square and disc-shaped workspaces. 
 \item Video  \emph{04Hardware Experiments.mp4} shows an experiment trial moving two particles to goal positions in a small intestine phantom, then an experiment trial using cow stomach tissue.
		\end{itemize}	 	
We also include four  Mathematica Notebooks (.nb files) containing simulation code.  
		   	\begin{itemize}	 
 \item   \emph{SquareWorkSpace.nb} generates paths in a square workspace for two particles.
 \item  \emph{CircularWorkSpace.nb} generates paths in a circular workspace for two particles.
 \item   \emph{DeltaConfigurationSpacePolygon.nb} generates the $\Delta$ configuration space for convex polygons
  \item   \emph{ShortestPathForADisk.nb} analytical solution for shortest path that touches a boundary from one position to another position in a circular workspace.
		\end{itemize}

### 2019-01-03 journalWallFriction/SwarmShapeControl.tex
added stubs for the final journal version.  Still need pictures

% And here is the link to the videos and summary and read me:
%  https://www.dropbox.com/home/BoundaryInteractionVideos
% difference between two pdf files: https://draftable.com/compare
%\documentclass[conference]{IEEEtran}
\documentclass[letterpaper, 10 pt, conference]{ieeeconf}
\IEEEoverridecommandlockouts% This command is only needed if 
                                                          % you want to use the \thanks command
%\overrideIEEEmargins                                      % Needed to meet printer requirements.
\usepackage{times}

@@

\newcommand{\revision}[1]{\textcolor{blue}{#1}}

@@

% paper title
\title{\LARGE \bf Exploiting Non-Slip Wall Contacts \\  to Position Two Particles Using The Same Control Input}

% You will get a Paper-ID when submitting a pdf file to the conference system
\author{Shiva Shahrokhi, Jingang Shi,  Benedict Isichei, and Aaron T. Becker% <-this % stops a space
\thanks{*This work was supported by the National Science Foundation under Grant No.\ \href{http://nsf.gov/awardsearch/showAward?AWD_ID=1553063}{ [IIS-1553063]}, \href{http://nsf.gov/awardsearch/showAward?AWD_ID=1619278}{[IIS-1619278]}, and  \href{https://nsf.gov/awardsearch/showAward?AWD_ID=1646566}{[CNS-1646566]}.}% <-this % stops a space
\thanks{Authors are with the Department of Electrical and Computer Engineering,  University of Houston, Houston, TX 77204 USA        {\tt\small  \{sshahrokhi2,atbecker\}@uh.edu}}%
}
%\affil{Department of Electrical and Computer Engineering, \\
% University of Houston, Houston, TX 77204-4005 USA\\
% {\tt\small  \{sshahrokhi2, aviswanathanmahadev, atbecker\}@uh.edu}}
%\thanks{S. Shahrokhi, A. Mahadev and  A. Becker are with the Department of Electrical and Computer Engineering,  University of Houston, Houston, TX 77204-4005 USA {\tt\small  \{sshahrokhi2, aviswanathanmahadev, atbecker\}@uh.edu}
%}
%} %\end thanks

@@

% KEYWORDS:   
% Underactuated Robots
% Motion Control
% Path Planning for Multiple Mobile Robot Systems
% Configuration Space
%	
%This is an extension of work presented in a preliminary conference paper:
%S. Shahrokhi, A. Mahadev, and A. T. Becker, ÒAlgorithms for shaping a particle swarm with a shared input by exploiting non-slip wall contacts,Ó in Intelligent Robots and Systems (IROS), 2017 IEEE/RSJ International Conference on, 2017.
\end{abstract}

@@

%%%%%%%%%%%%%%%
\input{intro}
%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%
\input{relatedWork}
%%%%%%%%%%%%%%%
\input{theory}
\input{theory2robAlgs}
%\input{theorynrobAlgs}
%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%
\input{simulation}
%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%
\input{experiment}
%%%%%%%%%%%%%%%
\input{conclusion}
%%%%%%%%%%%%%%%
%\section*{Acknowledgments}
%%%%%%%%%%%%%%%
%% Use plainnat to work nicely with natbib. 
{%\footnotesize
%\bibliographystyle{plainnat}
%\bibliographystyle{SageH}
\bibliographystyle{IEEEtran}
\bibliography{IEEEabrv,SwarmShapeControl}
}

% Uncomment to add appendix:
%\input{appendix}

>>>>

% And here is the link to the videos and summary and read me:
%  https://www.dropbox.com/home/BoundaryInteractionVideos
% difference between two pdf files: https://draftable.com/compare
%\documentclass[conference]{IEEEtran}
\documentclass[journal]{IEEEtran}
\IEEEoverridecommandlockouts% This command is only needed if 
                                                          % you want to use the \thanks command
%\overrideIEEEmargins                                      % Needed to meet printer requirements.
\usepackage{times}

@@

\newcommand{\revision}[1]{\textcolor{black}{#1}}  %changed to black for final

@@

% paper title
\title{Exploiting Non-Slip Wall Contacts  to Position\\ Two Particles Using The Same Control Input}

% You will get a Paper-ID when submitting a pdf file to the conference system
\author{Shiva Shahrokhi,~\IEEEmembership{Member,~IEEE,} Jingang Shi,  Benedict Isichei, and Aaron T. Becker,~\IEEEmembership{Senior Member,~IEEE,}% <-this % stops a space
\thanks{*This work was supported by the National Science Foundation under Grant No.\ \href{http://nsf.gov/awardsearch/showAward?AWD_ID=1553063}{ [IIS-1553063]}, \href{http://nsf.gov/awardsearch/showAward?AWD_ID=1619278}{[IIS-1619278]}, and  \href{https://nsf.gov/awardsearch/showAward?AWD_ID=1646566}{[CNS-1646566]}.}% <-this % stops a space
\thanks{Authors are with the Department of Electrical and Computer Engineering,  University of Houston, Houston, TX 77204 USA        {\tt\small  \{sshahrokhi2,atbecker\}@uh.edu}}%
\thanks{Manuscript received April 19, 2005; revised August 26, 2015.}}
%\affil{Department of Electrical and Computer Engineering, \\
% University of Houston, Houston, TX 77204-4005 USA\\
% {\tt\small  \{sshahrokhi2, aviswanathanmahadev, atbecker\}@uh.edu}}
%\thanks{S. Shahrokhi, A. Mahadev and  A. Becker are with the Department of Electrical and Computer Engineering,  University of Houston, Houston, TX 77204-4005 USA {\tt\small  \{sshahrokhi2, aviswanathanmahadev, atbecker\}@uh.edu}
%}
%} %\end thanks
\markboth{Journal of \LaTeX\ Class Files,~Vol.~14, No.~8, August~2015}%
{Shahrokhi \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for IEEE Journals}

@@

% KEYWORDS:   
% Underactuated Robots
% Motion Control
% Path Planning for Multiple Mobile Robot Systems
% Configuration Space
%	
%This is an extension of work presented in a preliminary conference paper:
%S. Shahrokhi, A. Mahadev, and A. T. Becker, ÒAlgorithms for shaping a particle swarm with a shared input by exploiting non-slip wall contacts,Ó in Intelligent Robots and Systems (IROS), 2017 IEEE/RSJ International Conference on, 2017.
\end{abstract}
\begin{IEEEkeywords}
Underactuated Robots, Motion Control, Path Planning for Multiple Robot Systems, Configuration Space.
\end{IEEEkeywords}

@@

%%%%%%%%%%%%%%%
\input{intro}
%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%
\input{relatedWork}
%%%%%%%%%%%%%%%
\input{theory}
\input{theory2robAlgs}
%\input{theorynrobAlgs}
%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%
\input{simulation}
%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%
\input{experiment}
%%%%%%%%%%%%%%%
\input{conclusion}
%%%%%%%%%%%%%%%
%\section*{Acknowledgments}
%%%%%%%%%%%%%%%
%% Use plainnat to work nicely with natbib. 
{%\footnotesize
%\bibliographystyle{plainnat}
%\bibliographystyle{SageH}
\bibliographystyle{IEEEtran}
\bibliography{IEEEabrv,SwarmShapeControl}
}
%Shiva Shahrokhi, Jingang Shi,  Benedict Isichei, and Aaron T. Becker
%
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{shiva.jpg}}]{Shiva Shahrokhi}(S`14) received M.S. and PhD degrees in the Electrical and Computer Engineering Department at the University of Houston in 2018.  
She received the B.S. degree in Computer Engineering from Iran University of Science and Technology,
Tehran, Iran. She is involved in studies of swarm manipulation and control for robotics applications.
These include steering massively under-actuated mobile robotic ensembles, swarm shape control, and machine learning.
\end{IEEEbiography}
%
\begin{IEEEbiography}{Jingang Shi}
Biography text here.
\end{IEEEbiography}
%
\begin{IEEEbiography}{Benedict Isichei}
received an M.S. degree in the Electrical and Computer Engineering Department at the University of Houston in 2018.
\end{IEEEbiography}
%
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{DrB.jpg}}]{Aaron T. Becker}(S`06-M`12-SM`17) received M.S. and PhD degrees in electrical and computer engineering from the University of Illinois at Urbana-Champaign, in 2008 and 2012. He was a post doctoral research scholar at the Multi-Robot Systems Lab at Rice University and at Boston Children's Hospital \& Harvard Medical School, before joining the Electrical and Computer Engineering Department at the University of Houston as an Assistant Professor in 2014. He won the best paper at IROS 2013 and received the NSF CAREER award in 2016. %He is active in developing control laws and algorithms for robot swarms.
\end{IEEEbiography}

### 2019-01-03 journalWallFriction/intro.tex
added stubs for the final journal version.  Still need pictures

\section{Introduction}\label{sec:Intro}
Particle swarms propelled by an external field, where each particle  receives the same control input, are common in applied mathematics, biology, and computer graphics \cite{Peyer2013,Shirai2005,Chiang2011}.
%
The small size of these robots makes it difficult to perform onboard computation.  Instead, these robots are often controlled by a broadcast signal. 
 The tiny robots themselves are often just rigid bodies, and it may be more accurate to define the robot as the \emph{system} that consists of particles, a uniform control field, and sensing.
  Consider a system of point-particles in a 2D planar workspace.
Such systems are severely underactuated, having 2 degrees of freedom in the shared planar control input, but $2n$ degrees of freedom for the $n$-particle swarm.
 Techniques are needed that can handle this underactuation.

>>>>

\section{Introduction}\label{sec:Intro}
\IEEEPARstart{P}{article} swarms propelled by an external field, where each particle  receives the same control input, are common in applied mathematics, biology, and computer graphics \cite{Peyer2013,Shirai2005,Chiang2011}.
%
The small size of these robots makes it difficult to perform onboard computation.  Instead, these robots are often controlled by a broadcast signal. 
 The tiny robots themselves are often just rigid bodies, and it may be more accurate to define the robot as the \emph{system} that consists of particles, a uniform control field, and sensing.
  Consider a system of point-particles in a 2D planar workspace.
Such systems are severely underactuated, having 2 degrees of freedom in the shared planar control input, but $2n$ degrees of freedom for the $n$-particle swarm.
 Techniques are needed that can handle this underactuation.
